\textbf{Adaptation of the PHQ-4 Short Screening for Depression and Anxiety to increase its Sensitivity to Subclinical Variability}

### 2023-01-07 analysis.Rmd
readme

See [**tutorial**](https://bookdown.org/bean_jerry/using_r_for_social_work_research/item-response-theory.html) on Item Response Theory (IRT).

https://aidenloe.github.io/introToIRT.html

>>>>

<!-- See [**tutorial**](https://bookdown.org/bean_jerry/using_r_for_social_work_research/item-response-theory.html) on Item Response Theory (IRT). -->

<!-- https://aidenloe.github.io/introToIRT.html -->

### 2023-01-07 paper/manuscript.Rmd
readme

The sample consists of 500 English-speaking participants (**stats**) who were administered the revised PHQ-4 online as part of another study, which data is available in open-access at https://github.com/RealityBending/IllusionGameReliability.

@@

```{r message=FALSE, warning=FALSE, out.width="100%"}
papaja::apa_table(
  data.frame(
    Facet = c("\\textbf{Anxiety}", "", "", "", "", "", "", "", "", "", "\\textbf{Depression}", "", "", "", "", "", "", "", "", ""),
    Item = c("Feeling nervous, anxious or on edge", "", "", "", "", "Not being able to stop or control worrying", "", "", "", "", "Little interest or pleasure in doing things", "", "", "", "", "Feeling down, depressed, or hopeless", "", "", "", ""),
    Response = paste0("\\textit{", rep(c("Not at all", "Once or twice", "Several days", "More than half the days", "Nearly every day"), 4), "}"),
    Basic_Scoring = rep(c("0", "0.5", "1", "2", "3"), 4),
    Normalized_Scoring = rep(c("0", "0.5", "0.7", "0.8", "1"), 4)
    ),
  caption = "Revised Patient Health Questionnaire-4 (PHQ-4R). The instructions are \"Over the last 2 weeks, how often have you been bothered by the following problems?\". The 0.5 scoring is introduced to preserve the compatibility with the original version, and enables to use its norms and cut-offs. The normalized scoring takes into account the non-linear spacing between item responses.",  
  escape = FALSE,
  font_size = "scriptsize",
  col.names = c("Facet", "Item", "Response", 
                "Basic Scoring", 
                "Normalized Scoring",
                "Scoring"),
  midrules = c(5, 10, 15))
```

>>>>

The sample consists of 500 English-speaking participants (**stats**) who were administered the refined PHQ-4 online as part of another study, which data is available in open-access at https://github.com/RealityBending/IllusionGameReliability.

@@

```{r message=FALSE, warning=FALSE, out.width="100%"}
papaja::apa_table(
  data.frame(
    Facet = c("\\textbf{Anxiety}", "", "", "", "", "", "", "", "", "", "\\textbf{Depression}", "", "", "", "", "", "", "", "", ""),
    Item = c("Feeling nervous, anxious or on edge", "", "", "", "", "Not being able to stop or control worrying", "", "", "", "", "Little interest or pleasure in doing things", "", "", "", "", "Feeling down, depressed, or hopeless", "", "", "", ""),
    Response = paste0("\\textit{", rep(c("Not at all", "Once or twice", "Several days", "More than half the days", "Nearly every day"), 4), "}"),
    Basic_Scoring = rep(c("0", "0.5", "1", "2", "3"), 4),
    Normalized_Scoring = rep(c("0", "0.5", "0.7", "0.8", "1"), 4)
    ),
  caption = "Refined Patient Health Questionnaire-4 (PHQ-4R). The instructions are \"Over the last 2 weeks, how often have you been bothered by the following problems?\". The 0.5 scoring is introduced to preserve the compatibility with the original version, and enables to use its norms and cut-offs. The normalized scoring takes into account the non-linear spacing between item responses.",  
  escape = FALSE,
  font_size = "scriptsize",
  col.names = c("Facet", "Item", "Response", 
                "Basic Scoring", 
                "Normalized Scoring"),
  midrules = c(5, 10, 15))
```
